Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2020-12-07 manuscript/draft_rsfmri.Rmd
added Lei_2019, Muschelli_2014 and Behzadi_2007

---
title: "Effects of bariatric surger and weight loss on resting-state functional connectivity"
author:
- xxx [1]
- xxx [1][2]
- xxx [1][2][3]
- xxx [1][2]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3
  Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book: 
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: yes
bibliography: "bibliography.bib"
editor_options: 
  chunk_output_type: console
---

@@

```{r "knit setup"}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
# set working directory of knit (RMarkdown) to directory of Rproj
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(knitr::opts_knit$get("root.dir"))
```

@@

<!-- DESCRIPTIVE STATISTICS --> The final sample entailed morbidly obese individuals (n = `r nrow(subj_df)`, `r nrow(filter(subj_df,Sex == "f"))` female; ages `r round(mean(subj_df$Age_BL),2)` $\pm$ `r round(sd(subj_df$Age_BL),2)` SD years (range `r min(subj_df$Age_BL)`-`r max(subj_df$Age_BL)`), that either underwent surgery (n = `r cs["Sum","KG"]`, `r cs["f","IG"]` female) or were waiting list controls (n = `r cs["Sum","KG"]`, `r cs["f","KG"]` female). The study design was quasi-experimental, as patient in the waiting control list had also been recommended to undergo bariatric surgery, but were still waiting for their health insurance's approval.
```{r baseline characteristics, include=FALSE}
dfBL <- txt_for_swe(group = "all", tp = "BL")

# distributions per group
# BMI 
p <- ggplot(data=dfBL, aes(group = condition, x=BMI, fill=condition)) +
  geom_density(alpha=0.6) + 
  scale_fill_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")) +
  theme_bw()
# log mean FD
p <- ggplot(data=dfBL, aes(group = condition, x=logmFD, fill=condition)) +
  geom_density(alpha=0.6) + 
  scale_fill_manual(
    values = c("#00305E55", "#C0004555"),
    labels = c("intervention", "control")) +
  theme_bw()
# Age
p <- ggplot(data=dfBL, aes(group = condition, x=Age_BL, fill=condition)) +
  geom_density(alpha=0.6) + 
  scale_fill_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")) +
  theme_bw()
tab_age <- psych::describeBy(data=dfBL, x=dfBL$Age_BL, group=dfBL$condition, mat=T)
# Sex
p <- ggplot(data = dfBL, aes(x = condition, fill = Sex)) + 
  geom_bar(position = "dodge") +
  scale_fill_manual(labels = c("female", "male"),
                    values = c("#00305E55", "#C0004555")
  )
tab_sex <- table(dfBL$condition, dfBL$Sex)
```
Histograms on baseline characteristics revealed, that patients in the control group did not differ notably from the intervention group regarding BMI and log mean FD, and only slightly in distribution of sex and age, the control group had a higher number of male participants (n = `r tab_sex[2,2]` vs. n = `r tab_sex[2,1]`) and a higher mean age (`r round(tab_age$mean[tab_age$group1=="KG"],2)` vs. `r round(tab_age$mean[tab_age$group1=="IG"],2)`).
<!-- SURGICAL PROCEDURE --> As intervention, $0$ participants received surgery that combines restrictive and malabsorptive mechanisms (RYGB) and $0$ surgery purely restricting energy intake (VSG: n = $0$, GB: n = $0$).
```{r tabdescr, echo=FALSE}

@@

Data preprocessing was conducted with FSL and Freesurfer using a nipype (version 14.0.2) workflow implemented in python 2.7. 
The preprocessing workflow included anatomical, functional and diffusion-weighted imaging preprocessing and wrapped modules from FSL version 6.0.1<!-- ?! -->, Freesurfer version 6.0.0p1, ANTS <!-- version?! and so on-->. Details have been published on github [https//:.???.com]()
<!-- anatomical preprocessing write something about anatomical preprocessing (Freesurfer etc.) here --> 
The T1-weighted image was segmented to remove non-brain tissue and together with the functional images normalized to a default brain template from the Monteal Neurological Institute (MNI) space. Functional images were smoothed with an $0$ mm FWHM Gaussian kernel.

<!-- minimal functional preprocessing --> Preprocessing pipeline included removal of first four volumes and a transformation of the blood oxygen level dependent (BOLD) time series into the subject's anatomical space. This transform combines parameters from motion correction (FSL's MCFLIRT), fieldmap distortion correction (based on fieldmap and FSL's FUGUE) and coregistration to the subject's anatomical template space (using Freesurfer's bbregister and the transform from individual to longitudinal template space in Freesurfer's longitudinal processing stream).

<!-- Aroma + CC/ + GSR --> Volumes were further preprocessed with ICA-AROMA and compCor (CC) and, optionally, with a subsequent global signal regression (GSR) [@Ciric_2017; @Parkes_2018] to reduce the effect of physiological noise and head motion on the connectivity estimates.
As global signal regression is very efficient in removing the correlation of head motion and connectivity dependence, but is known to introduces spatial dependency and spurious correlations, we performed GSR after ICA-AROMA in a separate sensitivity analysis.

### Seed region of interest (ROI)
<!-- Regions of interest (definition and transformation into freesurfer long space) --> Seed regions were ... mm spheres in the precuneus ((MNI)X,Y,Z = x,x,x) associated with the default mode network, and the Nucleus Accumbens (x,x,x) by averaging the time series across voxels.

### Connectivity maps
<!-- coregistration + normalization --> Voxel-wise seed-based connectivity maps in the individual subject's space (which was coregistered to the Freesurfer longitudinally preprocessed timepoint (more details)) were calculated using Pearson's correlation between average seed time series from pre-defined ROIs within the reward network (Nucleus accumbens, NAcc) and the DMN (precuneus, PCC). Subsequently, r-to-z transform was applied to the correlation to obtain normally distributed functional connectivity (using nilearn, nipype and python). 
Then, we will transform the connectivity maps into MNI space with a non-linear warp derived from anatomical preprocessing of the longitudinally preprocessed timepoints (using ANTS).

### Quality Assessment

>>>>

---
title: "Effects of bariatric surgery and weight loss on resting state functional connectivity"
author:
- Hannah Heinrichs* [1]
- Frauke Beyer* [1][2]
- Kerstin Prehn
- Agnes Floel
- Arno Villringer [1][2][3]
- A. Veronica Witte [1][2][3]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3
  Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book:
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: yes
bibliography: "bibliography.bib"
editor_options:
  chunk_output_type: console
---

@@

```{r "knit setup"}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex")
# set working directory of knit (RMarkdown) to directory of Rproj
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(knitr::opts_knit$get("root.dir"))
```
\newpage
# Abstract

\newpage
# Introduction
<!--Suggested Order of Introduction
1. Obesity is a major health concern. [... some more details about metabolic and mortality risk, especially related to morbid obesity ...] More and more recognized, midlie obesity also impacts later cognitive decline and dementia risk.
Obesity has been associated with differences in brain structure and function.
Regarding structural alterations, longitudinal studies have indicated that higher body mass index is related to increased cortial thinning in midlife (path through life study), potentially mediated by inflammation or glucose dysregulation... Similarly, white matter microstructure and may be related to adverse metabolic effects (lampe)
Differences in brain function in obesity have been reported in the reward network during task-based fMRI, highlighting the role of reward processing in obesity development and maintainance.
Resting state fMRI studies have also shown differences in connectivity in diverse brain networks, including reward and salience network, visual networks and the default mode network. In part, these differences have been related to metabolic and behavioral differences, yet there may be an important confounding due to head motion.
In this study, we aim to investigate the impact of bariatric surery on..
-->

<!-- obesity and interventions -->
Over the past decades, the global burden of obesity has increasingly been confronted as a matter of urgency by research.
_something about comorbidities_
Besides metabolic dysfunctions, obesity has been consistently associated with reduced gray matter volume, less intact white matter structure and reduced cognitive function [@Beyer_2019; @Zhang_2018].
Luckily, dietary interventions such as caloric restriction and related metabolic improvements, and weight loss have been suggested to improve neuronal plasticity and cognitive performance [@Witte_2009; @Zhang_2018; @Veronese_2017].
In some cases behavioral intervention fail to yield the desired success regarding weight loss. There are non-behavioral alternatives at hand.
<!-- bars most invasive (brain metabolism), last resort -->
Bariatric surgery is one promising option to combat morbid obesity, as it rapidly improves weight status, metabolic dysfunctions, and co-morbidities, such as diabetes [@]. Roux-en-Y gastric bypass (RYGB) is the most common procedure as it not only restricts the food intake by reducing stomach volume but also affects the absorption of macronutrients and the hormonal profile [@]. <!-- ref for "common", ref for procedure -->
Other widely used procedures are vertical sleeve gastrectomy (VSG) and gastric banding (GB) which only restrict food consumption. <!-- mehr zu Veränderung in Gasto-intestinaler Physiologie -->

<!-- Neural mechanisms/concurrent plasticity? -->
Precise mechanisms are yet to be elucidated. As a first step, a comprehensive understanding of the concurrent physiological changes underlying weight loss and recovery is needed. This will inform inferences about potential mechanisms and either support interventions proven to be effective or ideally allow imitating them will less invasive alternatives.

Recently, research focuses have slowly shifted to investigate brain metabolism structural and functional changes after surgery.
<!-- severe nutritional stress [@Crujeiras_2017] -->

<!-- Reward network -->
Little is known about the potential beneficial effects of bariatric surgery on brain function in the obese population, in particular with regard to hedonic motivations for food, which play a fundamental role in weight relapse.
<!-- mechanism reward and appetite, overating -->
Besides malabsorption and restricted food ingestion, patients report post-surgical changes in food preferences and eating behavior. Those psychophysiological and behavioral effects may be related to post-surgical changes in visceral sensory perceptions and endocrinological signaling. Corresponding information is processed by the fronto-mesolimbic system and affects appetite and reward signalling which may influence weight regulation [@Mulla_2017, @Nudel_2019].
<!-- results in lean -->
The reward network entailing the ventromedial prefrontal cortex (vmPFC), the striatum (STR) but also the anterior insula (antIns) has been linked to food valuation processes in decision-making in lean individuals [@Bartra_2013; @Hare_2011; @Hutcherson_2012; @Schmidt_2018; @Wiemerslage_2016].
<!-- results in obese longitudinal -->
Similarly, several studies have found differences in resting-state activity in reward regions depending on weight status.

Obese individuals exhibited increased connectivity between frontal and mesolimbic regions and weaker connectivity within regions of the mesolimbic system (encompassing limbic and striatal regions). These differences seemed to normalize, as trends reversed when looking at the resting state of obese individuals after compared to before the surgery [@Duan_2020].

On the other hand, BMI prior to the surgery was associated with changes in connectivity [@Duan_2020].

s concerning such processes following a surgical intervention are inconclusive.

<!-- important differences in the response to visual food-related cues between thin and reduced-obese individuals that place the latter group at an increased risk of  -->

<!-- Though there exists strong evidence for important differences in the .. between lean or normal-weight individuals and obese individuals, few studies have investigated the ... and even fewer compared reduced-obese individuals reduced-obese individuals -->
<!-- [@Garcia_Garcia_2012] -->

<!-- Default mode network -->
Weight regulation and energy expenditure is dependent on a complex interplay of external and internal sensory processing, as well as molecular homeostasis regulation. Obesity may be cause or effect of a decompensation of the psychophysiological system that ensures homeostasis.
The default mode network is commonly associated with processing of self-referent as well as introspective information, such as hunger sensation [@;@] and appetite [@Tregellas_2011]. <!-- parietal activation correlated with appetite measures after an overnight fast [@Tregellas_2011]. --> It is mainly composed of the posterior cingulate cortex (PCC)/precuneus, the medial prefrontal cortex (MPFC) and inferior and lateral parietal cortex (IPC, LPC; approx. BA 39) [@Raichle_2015]. The right ventral anterior cingulate cortex (VACC), superior frontal cortex (SFC), and inferior temporal cortex (ITC) show weaker but also reliable association with the PCC over the course of one year. Even broader conceptions count left VACC, middle temporal gyrus (MTG), and parahippocampal cortex, although associations with the PCC are not as stable [@Chou_2012].
<!-- difference lean obese -->
Functional connectivity of this network has been shown to be linked to BMI [@Beyer_2017] and altered after bariatric surgery [@Olivo_2016]. Generally, studies show an increased activation in the default mode network, especially in the precuneus and posterior cingulate cortex (PCC) in obese individuals [@Kullmann_2011; @].
A longitudinal study that confirmed the stronger connectivity (of PCC with anterior STG and anterior temporal fusiform gyrus and the Precuneus with the anterior STG). However, default mode connectivity in these regions seemed weakened over the course of one year. Because differences between lean controls and obese individuals that existed prebariatric surgery were no longer detectable 1 year after the surgery, the authors argue for a normalization in functional connectivity<!-- and PCC/PC connectivity with anterior STG are most affected by the surgery -->[@Olivo_2017].
This is consistent with other findings of reduction of functional connectivity of these and other regions of the default mode network, such as the VMPFC [@Li_2018] <!-- with the dorsolateral prefrontal cortex (DLPFC) --> after the surgery.

The exact mechanisms of how bariatric surgery affects functional plasticity needs to be investigated. Among patients undergoing surgery, change in BMI was negatively correlated with the changes in connectivity of the default mode network, namely between the PCC/precuneus and the DLPFC [@Li_2018].

On the other hand, connectivity also served as a predictor of weight loss after surgery.

On the other hand, there are also indicators of reduced functional integrity, e.g. for the anterior cingulate cortex (ACC) at resting state compared to lean individuals [@Kullmann_2011].

<!-- novelty statement --> As described previously, several studies have investigated the effects of bariatric surgery on the intrinsic functional connectivity in patients. Yet, to our knowledge there is no quasi-experimental study, comparing a cohort of patients to a cohort with similar characteristics but unexposed to the intervention, i.e. bariatric surgery, over an extended time period as would be demanded to draw more substantiated inference [@George_2016].
<!-- hypotheses --> In this study, we aim to bridge this gap and investigate possible dynamics of within-reward network connectivity before and after bariatric surgery by comparison with a contemporaneously measured waiting-control group. Moreover, we will explore whether the changes in functional connectivity are associated with the amount of weight lost after bariatric surgery treatment in obesity to explore a potential gradient link. In addition, we will investigate potential changes in within-network functional connectivity after surgery in other resting-state networks such as default mode network (DMN).
Participants are measured at baseline, at 6 months and at 24 months to capture both phases of rapid weight-loss and maintenance as expected from non-surgical interventions [@Shai_2008].

<!-- group effect because direct effect of intervention surgery -> rsfmri (cares lessfreq, less preoccupation with hunger, less/more reward sensitivity) vs. sugery -> BMI -> rsfmri (neural signalling, fatty tissue) -->

@@

<!-- DESCRIPTIVE STATISTICS --> The final sample entailed morbidly obese individuals (n = `r nrow(subj_df)`, `r nrow(filter(subj_df,Sex == "f"))` female; ages `r round(mean(subj_df$Age_BL),2)` $\pm$ `r round(sd(subj_df$Age_BL),2)` SD years (range `r min(subj_df$Age_BL)`-`r max(subj_df$Age_BL)`), that either underwent surgery (n = `r cs["Sum","KG"]`, `r cs["f","IG"]` female) or were waiting list controls (n = `r cs["Sum","KG"]`, `r cs["f","KG"]` female). The study design was quasi-experimental, as patient in the waiting control list had also been recommended to undergo bariatric surgery, but were still waiting for their health insurance's approval.
```{r test wd}
print(getwd())
```

```{r baseline characteristics, include=FALSE}
dfBL <- txt_for_swe(group = "all", tp = "BL")

# distributions per group
# BMI
p <- ggplot(data=dfBL, aes(group = condition, x=BMI, fill=condition)) +
  geom_density(alpha=0.6) +
  scale_fill_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")) +
  theme_bw()
# log mean FD
p <- ggplot(data=dfBL, aes(group = condition, x=logmFD, fill=condition)) +
  geom_density(alpha=0.6) +
  scale_fill_manual(
    values = c("#00305E55", "#C0004555"),
    labels = c("intervention", "control")) +
  theme_bw()
# Age
p <- ggplot(data=dfBL, aes(group = condition, x=Age_BL, fill=condition)) +
  geom_density(alpha=0.6) +
  scale_fill_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")) +
  theme_bw()

tab_age <- psych::describeBy(data=dfBL, x=dfBL$Age_BL, group=dfBL$condition, mat=T)

# Sex
p <- ggplot(data = dfBL, aes(x = condition, fill = Sex)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(labels = c("female", "male"),
                    values = c("#00305E55", "#C0004555")
  )
tab_sex <- table(dfBL$condition, dfBL$Sex)
```
Histograms on baseline characteristics revealed, that patients in the control group did not differ notably from the intervention group regarding BMI and log mean FD, and only slightly in distribution of sex and age, the control group had a higher number of male participants (n = `r tab_sex[2,2]` vs. n = `r tab_sex[2,1]`) and a higher mean age (`r round(tab_age$mean[tab_age$group1=="KG"],2)` vs. `r round(tab_age$mean[tab_age$group1=="IG"],2)`).
<!-- SURGICAL PROCEDURE --> As intervention, $0$ participants received surgery that combines restrictive and malabsorptive mechanisms (RYGB) and $0$ surgery purely restricting energy intake (VSG: n = $0$, GB: n = $0$).
```{r tabdescr, echo=FALSE}

@@

Imaging data was conducted using AFNI 19.1.05, ANTS '2.3.1', FSL '6.0.1' and FreeSurfer '6.0.0p1', wrapped in a nipype workflow (version 1.2.0) in Python 2.7.15.
The preprocessing workflow included modules to process anatomical, functional and diffusion-weighted imaging in parallel. The workflow can be found on [github](https://github.com/fBeyer89/ADI_preproc/).
### Anatomical preprocessing
Within the module for anatomical preprocessing, the T1-weighted images were first processed by FreeSurfer's cross-sectional pipeline [@fs_cross]. Then, Freesurfer's longitudinal stream was applied to all cross-sectional runs [@fs_long]. Here, white matter (WM) and cerebral spinal fluid (CSF) masks were derived based on FreeSurfer's `aseg.mgz` segmentation file for quality control of rs preprocessing.  
The skull-stripped brain (`brainmask.mgz`) was then coregistered to the MNI152 1x1x1x mm template using ANTS [@antsref]. The following parameters were used for rigid [metric: mutual information, number of iterations: [1000, 500, 250, 100]], affine [metric: mutual information, number of iterations: [1000, 500, 250, 100]] and SyN: [metric: cross-correlation, iterations: [100, 70, 50, 20]] registration steps with shrink factors [8, 4, 2, 1], and smoothing sigmas=[3, 2, 1, 0] for each step.
In the preregistration it was only mentioned that longitudinal FreeSurfer would be used, but no details regarding the exact analysis.

##Functional preprocessing
### Minimal functional preprocessing
The function preprocessing module included the removal of first four volumes, motion correction (FSL's `MCFLIRT`), fieldmap distortion correction (FSL's `fsl_prepare_fieldmap` and `FUGUE`) and coregistration to the subject’s individual longitudinal anatomical space (FreeSurfer's `bbregister`). In more detail, the transforms derived from the latter three steps were combined into one transformation.
For further analysis and ICA-AROMA processing, the data were intensity normalized and smoothed with a 6mm Gaussian kernel (`fslmaths -kernel gauss 2.548`).
This part of the analysis was described like "After removing the first four volumes, transforms for motion correction (FSL’s MCFLIRT), fieldmap distortion correction (based on fieldmap and FSL’s FUGUE) and coregistration to the subject’s individual anatomical space (using FREESURFER’s bbregister) are calculated." in the preregistration.
The resulting fMRI data is termed "minimally preprocessed" in the following.
### ICA-AROMA preprocessing
We used ICA-AROMA for fMRI denoising as it provides an acceptable trade-off between the mitigation of motion- FC correlation and the introduction of a distance-dependence on motion-FC relationship [@Parkes_2018]. The minimally preprocessed data was processed with independent component analysis (ICA) using FSL's `melodic` and nuisance components were classified according to four spectral and spatial criteria. Finally, the timeseries of the  nuisance components were regressed from the overall timeseries.
As recommended in the original paper, we performed regression of WM and CSF signal on the ICA-AROMA result. We used CompCor to estimate 5 variance components from a combined WM and CSF mask, which was further eroded using `fslmaths -nan -thr 0.99 -ero -bin` [@Behzadi_2007;@Muschelli_2014]. After regression of these nuisance components from the data, we performed high-pass filtering at 0.01 Hz.
This analysis was described in the preregistration as "Then we will employ state-of-the art nuisance regression (ICA-AROMA and CompCor regression of white matter and CSF signal to reduce the effect of physiological noise and head motion on the connectivity estimates."
### Global Signal regression
[@Ciric_2017] showed that GSR is very efficient in removing the correlation of head motion and FC, and outperforms ICA-AROMA alone. Yet, it introduces spatial dependency and spurious correlations. Previously, we reported on head motion differences between groups over time in this study [@Beyer_2020], and thus it was very important to minimize the motion-FC correlation. The global signal was derived from the average of all voxels in the brain mask. Then, we regressed WM and CSF CompCor components along with the GS from the ICA-AROMA fMRI data and high-pass filtered the resulting file as above.
In the preregistration we stated " As global signal regression is very efficient in removing the correlation of head motion and connectivity dependence, but introduces spatial dependency and spurious correlations, we perform GSR after ICA-AROMA in a separate sensitivity analysis."

### Functional connectivity
To derive reward and DMN functional connectivity maps, we used Nucleus Accumbens (Nacc) and precuneus as seed ROIs, respectively. Based on FreeSurfer's `aseg.mgz` and Desikan-Killiany parcellation, we created seed masks using `mri_binarize` (thresholded for NAcc at 26,58; precuneus at 1025,2025) and averaged them over hemispheres. Then, we used `NiftiLabelsMasker` and `NiftiMasker` to extract the standardized timeseries from the seed regions and the whole brain. We calculated the Pearson's correlation between them with `numpy.dot`, performed r-to-z transform and saved the resulting correlation maps for each processing mode (min, aroma+cc, aroma+gsr). Finally, the connectivity maps were transformed into MNI space using the affine transformation and non-linear warp derived during anatomical preprocessing.

### Quality Assessment
<!-- from Prereg -->

We will also extract mean and maximal framewise displacement (FD) from 6 translational/rotational motion parameters of the whole timeseries according to (Power et al., 2012) and calculate mean FD as a summary measure of head motion.

Whole brain FC maps will be calculated using Pearson’s correlation between average seed time series and whole brain timeseries on the subject level (using nilearn). After transforming from r-to-Z, we will transform the images into Freesurfer longitudinal space, using /mri/transforms/_to_.lta). Then, will calculate difference maps between BL-FU1 (confirmatory hypothesis), BL-FU2, FU1-FU2 (exploratory hypotheses). These images will be transformed into MNI space (using ANTS non-linear registration from the longitudinal template to MNI space) for statistical analysis.
Aggregated FC values will be calculated using Pearson’s correlation of average seed time series from pre-defined in the longitudinal template space. Aggregated values will be extracted for the reward and the default mode network.

Quality control:
- Freesurfer segmentations and surfaces will be visually controlled and corrected according to published recommendations, if necessary.
- Participants who cannot be correctly preprocessed due to (uncorrectable) artifacts in the T1-weighted or resting-state fMRI will be excluded.
-  We will first perfom the analysis with all participants who were correctly preprocessed. In a sensitivity analysis, participants with mean FD larger than the average mean FD + 2 standard deviations will be excluded.

We will also extract mean and maximal framewise displacement (FD) from 6 translational/rotational motion parameters of the whole timeseries according to (Power et al., 2012) and calculate mean FD as a summary measure of head motion.

-	Anthropometry: body mass index, % body fat from bioelectrical impedance measurement
-	Grouping variable is intervention versus control group
